A Fast Unified Model for Parsing and Sentence Understanding

### 2016-05-27 writing/hard_stack_paper/paper.tex
Summary of confusion matrix.

>>>>

Finally, as is likely inevitable for models evaluated on SNLI, all four models under study did several percent worse on test examples whose ground truth label is \textit{neutral} than on examples of the other two classes. \textit{entailment}--\textit{neutral} and \textit{neutral}--\textit{contradiction} confusions appear to be much harder to avoid than \textit{entailment}--\textit{contradiction} confusions, where relatively superficial cues might be more readily useful.
